Creating Diversity Input Objects

### 2024-09-03 code/L1/L1_LastStep_DiversityInputObjects.Rmd
update colors and change plot title, and other minor changes

# Plot Base Map
```{r}
basePlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly) +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest, fill = "forestgreen") +
  labs(title = "Tropical Andes", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

basePlot
ggsave("tropical_andes_forest_map.png", plot = last_plot(), path = figure_path)
```

# Plot points
```{r}
plantsPointsPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly) +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest, fill = "forestgreen") + 
  geom_sf(data = plants_sf_species, pch = 16, alpha = 0.1, size = 0.01) +
  labs(title = "Tropical Andes Plant Occurrences", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "tr", which_north = "true",
                         height = unit(0.5, "in"), width = unit(0.5, "in"),
                         pad_x = unit(0.1, "in"), pad_y = unit(0.1, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

@@

```{r}
frugivoresPointsPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly) +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest, fill = "forestgreen") +
  geom_sf(data = frugivores_sf_species, pch = 16, alpha = 0.1, size = 0.01) +
  labs(title = "Tropical Andes Frugivore Occurrences", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "tr", which_north = "true",
                         height = unit(0.5, "in"), width = unit(0.5, "in"),
                         pad_x = unit(0.1, "in"), pad_y = unit(0.1, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))
frugivoresPointsPlot
#ggsave("frugivore_occurrence_points_map.png", plot = last_plot(), path = figure_path)
```

>>>>

# Plot Base Map
```{r}
basePlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly) +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest, fill = "#D9F7D9") +
  labs(title = "Tropical Andes Forest", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.3, style = "ticks") +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

basePlot
#ggsave("tropical_andes_forest_map.png", plot = last_plot(), path = figure_path)
```

# Plot points
```{r}
plantsPointsPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly) +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest, fill = "#D9F7D9") + 
  geom_sf(data = plants_sf_species, pch = 16, size = 0.05) +
  labs(title = "Fruiting Plant Occurrences", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl",width_hint = 0.3, style = "ticks") +
  annotation_north_arrow(location = "tr", which_north = "true",
                         height = unit(0.5, "in"), width = unit(0.5, "in"),
                         pad_x = unit(0.1, "in"), pad_y = unit(0.1, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

@@

```{r}
frugivoresPointsPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly) +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest, fill = "#D9F7D9") +
  geom_sf(data = frugivores_sf_species, pch = 16, size = 0.01) +
  labs(title = "Frugivore Occurrences", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl",width_hint = 0.3, style = "ticks") +
  annotation_north_arrow(location = "tr", which_north = "true",
                         height = unit(0.5, "in"), width = unit(0.5, "in"),
                         pad_x = unit(0.1, "in"), pad_y = unit(0.1, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))
frugivoresPointsPlot
#ggsave("frugivore_occurrence_points_map.png", plot = last_plot(), path = figure_path)
```
